cardinalR: Generating interesting high-dimensional data structures

### 2025-04-30 paper-cardinalR.Rmd
Updated multicluster

```{r}
branch_tb <- tibble(fun = c("gen_expbranches",
                             "gen_linearbranches",
                             "gen_curvybranches", 
                             "gen_orglinearbranches", 
                             "gen_orgcurvybranches"), 
                      exp = c("",
                               "", 
                               "",
                               "",
                               ""))
```

@@

```{r data-bluntedcone}
bluntedcone <- gen_bluntedcone(n = 1000, p = 4, h = 5, ratio = 0.5)
```

```{r, eval=FALSE}
langevitour::langevitour(bluntedcone)
```

@@

## To generate data
five_clusts <- gen_multicluster(n = c(2250, 1500, 750, 1250, 1750), p = 4, k = 5,
                       loc = positions,
                       scale = c(0.4, 0.35, 0.3, 1, 0.3),
                       shape = c("helicalspiral", "hemisphere", "unifcube", 
                                 "bluntedcone", "gaussian"),
                       rotation = NULL,
                       is_bkg = FALSE)
```

>>>>

```{r}
branch_tb <- tibble(fun = c("gen_expbranches",
                             "gen_linearbranches",
                             "gen_curvybranches", 
                             "gen_orglinearbranches", 
                             "gen_orgcurvybranches"), 
                      exp = c("Generate a structure with exponential shaped branches.",
                               "Generate a structure with linear shaped branches.", 
                               "Generate a structure with curvy shaped branches.",
                               "Generate a structure with linear shaped branches originated in one point.",
                               "Generate a structure with curvy shaped branches originated in one point."))
```

@@

```{r data-bluntedcone}
cone <- gen_cone(n = 1000, p = 4, h = 5, ratio = 0.5)
```

```{r, eval=FALSE}
langevitour::langevitour(cone)
```

@@

## To generate data
five_clusts <- gen_multicluster(n = c(2250, 1500, 750, 1250, 1750), p = 4, k = 5,
                       loc = positions,
                       scale = c(0.4, 0.35, 0.3, 1, 0.3),
                       shape = c("helicalspiral", "hemisphere", "unifcube", 
                                 "cone", "gaussian"),
                       rotation = NULL,
                       is_bkg = FALSE)
```
